Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-02-17 Thesis/chapter/062-post-emma.tex
lin reg

\subsection{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Linear Regression}
I thought that the influence of $c_{zr}$ and $\lambda$ are the biggest, but they are the smallest absolute values. 
Thus, even though $T_{cal}$ might have a smaller coefficient for linear reg, the influence on the dependent variable might be larger. 
The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
Both $T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance. 
Then both $\lambda$ and $v_{DB}$ both have about a fifth ob the largest influence and a negative influence. 
An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $G$, 0.34. 
The coefficients, though share the signs. 
This is only true if the extended data set is used and therefore again rather by chance. 
It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}.

$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality.

\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}

Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.

>>>>

\subsection{Post-EMMA}
\label{sec:res-post-emma}
%describe what awaits the reader in this chapter:
In this section the experimental results are analyzed with different methods and compared with the original method EMMA which was integrated into the experiment selection process. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
%\textbf{EMMA}
The \gls{rf}s produced by the last iteration of \gls{emma} (see equations \ref{eq:emma-phd4} and \ref{eq:emma-G4}) put a high significance
%/effect/correlation
on the calcination temperature $T_{cal}$ with regard to the 
measures of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data 
%\td{ANOVA was used to check if \gls{bf} identified by \gls{emma} are reasonable.}

@@

%%%%%%%%%%%%%%%%%%%% LIN REG %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{Linear Regression} 
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by the Zirconium concentrain in the starting solution $c_{zr}$ and the number of layers applied $\lambda$, but their coefficients are the smallest in absolute values. 
The coefficients of
the Zirconium concentration in the starting solution $c_{zr}$ and the number of layers applied $\lambda$ are largest in value, but the values which are taken by $c_{zr}$ and $\lambda$ are the smallest among the input variables. 
%Initially, it was thought that the resulting layer and thus resistance of a sample is mainly influennced by
%but their coefficients are the smallest in absolute values. 
%
\begin{align}
	\begin{split}
		\label{eq:linreg-phd}
		\hat{\rho} =&  -0.022\cdot c_{zr} -0.022\cdot \lambda -0.0029\cdot v_{DB} + 0.0058\cdot T_{DB} \\
		& -8.5\cdot 10^{-5}\cdot v_{cal} + 0.0026\cdot T_{cal} -0.76
	\end{split}
	\\
	\begin{split}
		\label{eq:linreg-G}
		\hat{\gamma} ={} & 3.2\cdot c_{zr} - 0.97\cdot \lambda - 1.2\cdot v_{DB} + 0.2\cdot T_{DB} \\
			& - 0.014\cdot v_{cal} + 0.13\cdot T_{cal} + 7.2
	\end{split}
\end{align}
%
All terms have the same signs in equations \ref{eq:linreg-phd} and \ref{eq:linreg-G} have the same sign except the intercept and $c_{zr}$. 
$T_{cal}$ and $T_{DB}$ have positive coefficients, i.e. a negative influence on the resistance 
and $\lambda$,$v_{DB}$ and $v_{cal}$ have negative coefficients, i.e. a positive influence on resistance. 
An indication that the data is strongly tainted by error (see also section \ref{sec:res-anova}) is the low $R^2$ score of 0.41 of $\hat\rho$, 
which is (sad but true) even undercut by the $R^2$ of linear fit of $\hat\gamma$, 0.34. 
%The coefficients, though share the signs. 
%This is only true if the extended data set is used and therefore again rather by chance. 
When the linear regression is trained on the complete data set, all terms have the same sign. 
%It is even more astounding that \gls{emma} managed to decrease the average of $\gamma$ an $\rho$ with each generation (see figure \ref{fig:emma-gen}. 
%
\begin{table}[htb]
	\center
	\begin{tabular}{cccccccc}
		        & $c_{zr}$      & $\lambda$     & $v_{DB}$      & $T_{DB}$      & $v_{cal}$     & $T_{cal}$\\
				\hline\hline
				$\rho$          &2.04   &46.58  &1.15   &9.21   &13.50  &27.52\\
				$\gamma$        &10.24  &7.10   &16.46  &10.97  &7.68   &47.55\\
				\hline\hline
	\end{tabular}
	\label{tab:lin-reg-influence}
	\caption{Influences of input variables on output variables in percent according to linear regression.}
\end{table}
%
Thus, even though $T_{cal}$ might have a smaller coefficient in the linear \gls{rf}, the influence on the dependent variable might be larger. 
The influence was calculated by the formula: $I_i=\frac{\bar{x}_i \cdot k_i}{\sum_i \bar{x}_i \cdot k_i}$ with $i=1,\dots,d $ and where $\bar{x}_i$ is average value of the $i$-th input variable and $k_i$ is the coefficient of the $i$-th input variable in the linear regression. 
%The biggest influence on $\rho$ is indeed $T_{cal}$, next with about a third of the influence $T_{DB}$. 
The biggest influence on $\hat\rho$ and $\hat\gamma$ are $\lambda$ and $T_{cal}$. 
While $T_{cal}$ is the second largest influence on $\hat\rho$ as well it is noteworthy that $\lambda$ contributes the least to $\hat\gamma$. 
Furthermore the influence on $\hat\rho$ is dominated by $\lambda$ and $T_{cal}$, while the influences on $\hat\gamma$ are distributed more evenly.
Different distributions were not expected. 
This can have two reasons: 
either the *optimizands* darstellen differen properties and/or signal to noise ratio is too low.
%

$v_{cal}$ and $\lambda$ are well predicted by linear regression as there is a perfect direct proportionality. 
%Do multi linear reg like in Peprah et al. 2017\cite{peprah2017appraisal}.
%
